Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Add repo for XFOIL coeffs; resolves #19
Add references on CFT wake studies

@@

\todo[inline]{Examples of very low $Re$ CFT work, e.g. Brochier et al.?}

@@

Results from the XFOIL calculations are shown in Figure~\ref{fig:foil-Re-dep},
where values of maximum lift coefficient, minimum drag coefficient, and maximum
lift-to-drag ratio are normalized (for comparison between foils) and plotted
versus $Re_c$. In general, larger camber is associated with decreased foil
performance at lower Reynolds number.

>>>>

The wake of a cross-flow turbine in dynamic stall has been studied via laser
Doppler velocimetry by Brochier et al. \cite{Brochier1986} and with particle
image velocimetry (PIV) by Fujisawa and Shibuya \cite{Fujisawa2001}. However,
both of these studies were performed at very low Reynolds numbers---$Re_D =
10^4$ and $10^3$, respectively. Tescione et al. \cite{Tescione2014} studied the
wake of a vertical-axis wind turbine in a wind tunnel using stereo PIV at an
approximate blade chord Reynolds number $Re_c = 1.7 \times 10^5$; very close to
the $Re$-independent state reported in \cite{Bachant2014}.

@@

@@

Results from the XFOIL calculations are shown in Figure~\ref{fig:foil-Re-dep},
where values of maximum lift coefficient, minimum drag coefficient, and maximum
lift-to-drag ratio are normalized (for comparison between foils) and plotted
versus $Re_c$. In general, larger camber is associated with decreased foil
performance at lower Reynolds number. The data and processing code for these
calculations is available from \cite{Bachant2015-NACAXX20-XFOIL}.
